### 2017-08-17 paper/incomeShocks-jde-r1.tex
Add contraceptive's effect on pregnancy table

\begin{table}[htbp]
\begin{center}
\begin{threeparttable}
\caption{Contraceptive Use and Pregnancy}
\label{tab:effectiveness}
\begin{tabular}{@{} l  D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6}  @{}}
\toprule
                                                       & \multicolumn{3}{c}{Currently Pregnant} \\ \cmidrule(lr){2-4}
                                                       &\mco{Any}            & \mco{Traditional}   & \mco{Modern}        \\ \midrule
Contraceptives (7 months)                              &       0.174\sym{**} &       0.161\sym{**} &       0.300\sym{*}  \\
                                                       &     (0.067)         &     (0.066)         &     (0.167)         \\
Crop loss (7-14 months) \X Any Contraceptive (7 months)&      -0.253\sym{**} &      -0.254\sym{**} &      -0.314         \\
                                                       &     (0.110)         &     (0.113)         &     (0.235)         \\
Crop loss - 7-14 months (200 TZS or above)             &       0.047         &       0.039         &       0.031         \\
                                                       &     (0.051)         &     (0.052)         &     (0.049)         \\
\addlinespace 
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Observations                                           &    \mco{741}        &    \mco{741}        &    \mco{741}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
% All values of crop lost and assets are per capita and measure in 1,000 TZS.
% Variables not shown: Age of mother and number of births.
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

>>>>

% Table with contraceptive use effect on pregnancy
\input{../tables/main_effectiveness.tex}
